Supporting Information\\ \textit{Cross Validation Approaches for Penalized Cox Regression}

### 2019-12-06 main.tex
add correlated case to supporting materials

\subsection{Power}
\label{Sec:power}
While cross-validation is mainly a measure of the model's predictive accuracy, it is not sufficient to only compare those methods based on predictive accuracy. Another important criterion is that how many important variables are correctly selected by the model. The following simulations are conducted to compare the methods in this aspect.

>>>>

\bnote{Simulations with features that has more complicated correlation structures were conducted as well. Similar patterns were observed as in Figure~\ref{Fig:mse-brier-c} and Table~\ref{Tab:sim}. Results of these simulations are provided in the supporting document.}

\subsection{\bnote{Power}}
\label{Sec:power}

While cross-validation is mainly a measure of the model's predictive accuracy, it is not sufficient to only compare those methods based on predictive accuracy. Another important criterion is that how many important variables are correctly selected by the model. The following simulations are conducted to compare the methods in this aspect.

### 2019-12-06 supplementary.tex
Submitted to Statistics in Medicine
add correlated case to supporting materials

\title{Supplementary Material\\
\textit{Cross Validation Approaches for Penalized Cox Regression}}

@@

\section{Cross-Validated Deviance Residuals}

The Cox model implies the following relationship between the baseline cumulative hazard and the cumulative hazard for individual $i$:
\begin{equation}
  \hat{\Lambda}_{i}(t) =  \hat{\Lambda}_{0}(t)\exp(X_i\Tr\hat\beta).
\end{equation}
Consider the following approach: for fold $k$, we obtain $\hat{\beta}^{-k}$ from the training set $T_k$ and then for each $i$ in the test set $D_k$, 
\begin{equation}
 \label{eq:cv-bhz}
  \hat{\Lambda}^{cv}_{i}(t) =  \hat{\Lambda}_{0}(t)\exp(X_i\Tr\hat\beta^{-k}).
\end{equation}

@@

\section{Baseline Estimations}

	\subsection{Nelson-Aalen Estimator}
	 The simplest approach to estimating the cumulative baseline hazard, $\Lambda_0$, is the Nelson-Aalen Estimator \citep{nelson1969, aalen1978}:
\begin{equation}
  \hat{\Lambda}_{0}(t) = \sum_{t_j \leq t}\frac{\text{number of failures at time } t_j}{\text{number at risk right before time }t_j}.
\end{equation}
	The Nelson-Aalen Estimator does not involve any information from the covariates. It only depends on the failure times.

	\subsection{Kalbfleisch and Prentice's Approach}					
	\cite{Kalbfleisch2011} proposed a cumulative hazard estimator that incorporates covariates. Assuming only a single failure occurs at $t_i$, based on the fitted values of $\hat{\bbeta}$, we can first compute linear predictors $\hat{\eta}_i$ at each observed failure time. Based on $\hat{\eta}_i$, we can compute a discrete hazard component at each observed failure time):
\begin{equation}
1 - \hat{\alpha}_{i} = 1 - \left\{ 1 - \frac{\exp (\hat{\eta}_{i})}{\sum_{ j \in R(t_{i})}exp (\hat{\eta}_{j}} \right\}^{exp(-\hat{\eta}_{i})},
\end{equation}
and aggregate them together into the cumulative hazard function:
\begin{equation} 
\hat{\Lambda}_0(t) = \sum(1 - \hat{\alpha}_i)\mathds{1}(t_{i} \leq t),
\end{equation}

\section{Simulation Comparison}
The following simulation illustrates how the performance of cross-validated deviance residuals would vary based on different baseline estimation. We generated data using the same mechanism as we described in Section 3.1 in the paper. In each simulated data set, there were $n = 150$ observations, $p = 1000$ number of feature and 10 non-zero features with signal strength $s$. Censoring proportion is fixed at $10\%$. For each scenario, we varied $s$ from 0.4 to 0.9 and 200 replications were used. We compared the cross-validated deviance residuals constructed by Nelson-Aalen estimator and the cross-validated deviance residuals constructed by Kalbfleisch and Prentice's estimator. We also included cross-validated linear predictor approach (introduced in Section 2.3 in the paper) for comparison. The results of the simulation is listed in the following table:

@@

\bibliographystyle{abbrvnat}

\bibliography{articles}

>>>>

\title{Supporting Information\\
\textit{Cross Validation Approaches for Penalized Cox Regression}}

@@

\section{Baseline Estimation for Cross-Validated Deviance Residuals}
\subsection{Cross-Validated Deviance Residuals}
The Cox model implies the following relationship between the baseline cumulative hazard and the cumulative hazard for individual $i$:
\begin{equation}
  \hat{\Lambda}_{i}(t) =  \hat{\Lambda}_{0}(t)\exp(X_i\Tr\hat\beta).
\end{equation}
Consider the following approach: for fold $k$, we obtain $\hat{\beta}^{-k}$ from the training set $T_k$ and then for each $i$ in the test set $D_k$, 
\begin{equation}
 \label{eq:cv-bhz}
  \hat{\Lambda}^{cv}_{i}(t) =  \hat{\Lambda}_{0}(t)\exp(X_i\Tr\hat\beta^{-k}).
\end{equation}

@@

\subsection{Baseline Estimations}

	\subsubsection{Nelson-Aalen Estimator}
	 The simplest approach to estimating the cumulative baseline hazard, $\Lambda_0$, is the Nelson-Aalen Estimator \citep{nelson1969, aalen1978}:
\begin{equation}
  \hat{\Lambda}_{0}(t) = \sum_{t_j \leq t}\frac{\text{number of failures at time } t_j}{\text{number at risk right before time }t_j}.
\end{equation}
	The Nelson-Aalen Estimator does not involve any information from the covariates. It only depends on the failure times.

	\subsubsection{Kalbfleisch and Prentice's Approach}					
	\cite{Kalbfleisch2011} proposed a cumulative hazard estimator that incorporates covariates. Assuming only a single failure occurs at $t_i$, based on the fitted values of $\hat{\bbeta}$, we can first compute linear predictors $\hat{\eta}_i$ at each observed failure time. Based on $\hat{\eta}_i$, we can compute a discrete hazard component at each observed failure time):
\begin{equation}
1 - \hat{\alpha}_{i} = 1 - \left\{ 1 - \frac{\exp (\hat{\eta}_{i})}{\sum_{ j \in R(t_{i})}exp (\hat{\eta}_{j}} \right\}^{exp(-\hat{\eta}_{i})},
\end{equation}
and aggregate them together into the cumulative hazard function:
\begin{equation} 
\hat{\Lambda}_0(t) = \sum(1 - \hat{\alpha}_i)\mathds{1}(t_{i} \leq t),
\end{equation}

\subsection{Simulation Comparison}
The following simulation illustrates how the performance of cross-validated deviance residuals would vary based on different baseline estimation. We generated data using the same mechanism as we described in Section 3.1 in the paper. In each simulated data set, there were $n = 150$ observations, $p = 1000$ number of feature and 10 non-zero features with signal strength $s$. Censoring proportion is fixed at $10\%$. For each scenario, we varied $s$ from 0.4 to 0.9 and 200 replications were used. We compared the cross-validated deviance residuals constructed by Nelson-Aalen estimator and the cross-validated deviance residuals constructed by Kalbfleisch and Prentice's estimator. We also included cross-validated linear predictor approach (introduced in Section 2.3 in the paper) for comparison. The results of the simulation is listed in the following table:

@@

\section{Simulation with Correlated Features}

Simulations in this section are conducted to examine how correlations among features can impact the performance of the cross-validation approaches.

The data generating mechanism is similar to simulations presented in Figure 2 in the manuscript, except that each non-zero feature is correlated with 10 null features. We considered two types of correlation structures: exchangeable and autoregressive. We simulated data with a spectrum of correlation, from 0 to 0.8. Results of the simulation is presented in Figure~\ref{Fig:ex} for exchangeable correlation structure and Figure~\ref{Fig:auto} for autoregressive correlation structure.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{manuscript_figure/figure_2_ex.png}
  \caption{\label{Fig:ex} The horizontal axis in all three plots is the correlation among the features. The value of $s$ is varied from 0.4 to 0.9.  $\log(\text{MSE ratio})$, relative to the oracle modle is plotted in the left panel. Out-of-sample Brier scores are plotted in the middle. Out-of-sample C index is plotted in the right panel. For each simulated data set, n = 120, p = 1000. Expected censoring percentage is 10$\%$.}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{manuscript_figure/figure_2_auto.png}
  \caption{\label{Fig:auto} The horizontal axis in all three plots is the correlation among the features. The value of $s$ is varied from 0.4 to 0.9.  $\log(\text{MSE ratio})$, relative to the oracle modle is plotted in the left panel. Out-of-sample Brier scores are plotted in the middle. Out-of-sample C index is plotted in the right panel. For each simulated data set, n = 120, p = 1000. Expected censoring percentage is 10$\%$.}
\end{figure}

As is shown in the figures, across different correlation structure and strength of the correlation, the basic approach and the linear predictor appraoch had the best performance of having lower MSE, smaller Brier scores and higher C Index, whereas the V$\&$VH approach has the worst performance.

\bibliographystyle{abbrvnat}
\bibliography{articles}
